An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-10-24 neurips-19/poly-embed.tex
Fixed typos in proposed additions

\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computer once.  They are generally derived mathematically, rather than computationally.  These symbolically calculations typically tend to be straightforward, but can sometimes be tricky.}

>>>>

\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.  They are generally derived mathematically, rather than computationally.  These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
